\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-0mm}

### 2023-12-02 text/proposta/prop.tex
Proposal
final

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal \\ \vspace{0mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-0mm}}
\date{November 2023}

@@

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/scheme.jpeg}
  \captionof{figure}{Experimental set-up.}
\label{fig:setup}
\end{center}

@@

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/Li_crosssection_energy.jpeg}
  \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy.}
\label{fig:crosssection}
\end{center}

We are only interested in the energy range of $[0.5,5]$ MeV because the energy of the beam is limited by the accelerator.
As we can see in figure \ref{fig:crosssection}, the cross section of the reaction is maximum in the $[2.5,3]$ MeV range. 
Therefore, since we want to detect the Li-7 in the samples, we should choose the energy of the beam to be in this range.

>>>>

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-0mm}}
\date{November 2023}

@@

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/scheme.jpeg}
  \captionof{figure}{Experimental set-up.}
  \label{setup}
\end{center}

@@

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/Li_crosssection_energy.jpeg}
  \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy.}
  \label{crosssection}
\end{center}

We are only interested in the energy range of $[0.5,5]$ MeV because the energy of the beam is limited by the accelerator.
As we can see in figure \ref{crosssection}, the cross section of the reaction is maximum in the $[2.5,3]$ MeV range. 
Therefore, since we want to detect the Li-7 in the samples, we should choose the energy of the beam to be in this range.
